Function multiversioning in system image

### 2017-10-17 presentations/2017-10-17_julia-mv/present.tex
[presentations/2017-10-17_julia-mv] done?

% Story
% * openlibm performance issue

@@

@@

>>>>

% openlibm performance issue
% Not only does this trigger the chain of events that led me to implement this PR
% but it's also another example of interaction between code compiled for different archs.

% Processors shouldn't remember the history and decide how fast to run
% Except that it does....

@@

% Larger address space / more data simultaneously
% Issue caused by mixing YMM aware Glibc code and legacy code using XMM in openlibm.

@@

\begin{frame}{Compile openlibm for AVX (ymm registers)}
  \begin{itemize}
  \item<+-> GCC function attribute \textit{target\_clone}\\
    \ldots specify that a function be cloned into multiple versions
    compiled with different target options \ldots It also creates a resolver function (\ldots)
    that dynamically selects a clone suitable for current architecture \ldots\\\vspace{0.5cm}
  \item<+-> Has bug on current GCC versions so not usable in openlibm.\\
    But it's a good start.
  \end{itemize}
\end{frame}

\begin{frame}{Why function multiversioning}
  \begin{itemize}
  \item<+-> For code in the system image\\\vspace{0.1cm}
  \item<+-> For JIT code\\\vspace{0.1cm}
    \visible<+->{JIT features > system image features}\\\vspace{0.1cm}
    \visible<+->{JIT register size == system register size}
  \end{itemize}
\end{frame}

\begin{frame}{Cloning}
  \begin{center}
    \begin{tikzpicture}
      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-5, 2) (f0) {test\_f};
      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (0, 2) (g0) {test\_g};
      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (5, 2) (h0) {test\_h};
      \draw[->, line width=1.4] (g0) edge (f0);
      \visible<1> {
        \draw[->, line width=1.4] (h0) edge (g0);
      }

      \visible<2-> {
        \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-5, -2) (f1) {test\_f.clone};
        \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (0, -2) (g1) {test\_g.clone};
        \draw[->, line width=1.4] (g1) edge (f1);
      }
      \visible<2> {
        \draw[->, red, line width=1.4] (h0) edge (g0);
      }

      \visible<3> {
        \node[fill=orange!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (1, 0) (gg) {test\_g.slot};
        \draw[->, blue, line width=1.4] (h0) edge (gg);
        \draw[->, dashed, line width=1.4] (gg) edge (g0);
        \draw[->, dashed, line width=1.4] (gg) edge (g1);
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Next step}
  \begin{block}{}
    \begin{itemize}
    \item<+-> Expose user API\\\vspace{0.2cm}
      \begin{itemize}
      \item<+-> Platform agnostic, e.g. ``fma''\\\vspace{0.2cm}
      \item<+-> Platform specific, e.g. ``x86::avx2''\\\vspace{0.2cm}
      \end{itemize}\\\vspace{0.2cm}
    \item<+-> Make use of this in other part of runtime\\\vspace{0.2cm}
      \visible<+->{crc32c, PLT, \ldots}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{}
\end{frame}
